
\subsection{Course Introduction}

This subsection provides an overview of the course, highlighting its core objectives, prerequisites, and available resources. The course aims to equip students with the necessary skills to effectively utilize simulation in various applications.

\subsubsection{Course Objectives}
The primary objectives of the course are as follows:
\begin{itemize}
    \item \textbf{Simulation Models:} 
    \begin{itemize}
        \item Identify and recognize different simulation models and studies.
        \item Understand their applications across various fields.
    \end{itemize}
    \item \textbf{Simulation Languages:} 
    \begin{itemize}
        \item Illustrate the structure and organization of simulation languages.
        \item Focus on modeling with Arena, which provides advanced simulation and animation capabilities.
    \end{itemize}
    \item \textbf{Statistical Aspects:} 
    \begin{itemize}
        \item Concentrate on key statistical components of simulations, including:
        \begin{itemize}
            \item Input analysis
            \item Random variable generation
            \item Variance reduction techniques
        \end{itemize}
    \end{itemize}
\end{itemize}

% Challenges and Limitations
\textit{Challenges:} Understanding the statistical aspects may require additional study, especially for those less familiar with probability and statistics.

\subsubsection{Prerequisites and Resources}
To succeed in this course, students should meet the following prerequisites and utilize the recommended resources:
\begin{itemize}
    \item \textbf{Prerequisites:} 
    \begin{itemize}
        \item A solid foundation in probability and statistics, ideally at the level of introductory courses.
        \item Familiarity with programming languages and spreadsheet software.
    \end{itemize}
    \item \textbf{Resources:} 
    \begin{itemize}
        \item Recommended texts include:
        \begin{itemize}
            \item Law's "Simulation Modeling and Analysis" (5th edition or earlier)
            \item Kelton's work on Arena (6th edition or earlier)
        \end{itemize}
        \item Access to extensive course notes and free Arena software is provided to facilitate learning.
    \end{itemize}
\end{itemize}

% Challenges and Limitations
\textit{Limitations:} Some resources may be costly, and students should be prepared to engage with the software and course materials actively.

% mdframe suggestion
\begin{mdframed}[style=detailsstyle]
\textbf{Deep Dive: Simulation Models}
Explore various types of simulation models and their applications in real-world scenarios.
\end{mdframed}
