
\subsection{Practical Examples and Applications}

Simulation plays a crucial role in various fields by providing insights into complex systems and processes. This section explores practical examples and applications of simulation, highlighting their significance and impact.

\subsubsection{Basic Examples}
\begin{itemize}
    \item \textbf{Monte Carlo Simulation:} 
    \begin{itemize}
        \item Utilizes random sampling to estimate mathematical functions and simulate the behavior of various systems.
        \item Example: Estimating the value of $\pi$ through random point generation within a unit square.
    \end{itemize}
    
    \item \textbf{Queuing Models:} 
    \begin{itemize}
        \item Analyze customer flow in service systems to improve efficiency and reduce wait times.
        \item Example: Modeling customer arrivals and service times at a bank to optimize staffing levels.
    \end{itemize}
\end{itemize}

\subsubsection{Advanced Applications}
\begin{itemize}
    \item \textbf{Stock Market Simulation:} 
    \begin{itemize}
        \item Simulates stock portfolios to analyze market behavior, assess risk, and develop investment strategies.
        \item Example: Using historical data to model stock price movements and predict future trends.
    \end{itemize}
    
    \item \textbf{Random Number Generation:} 
    \begin{itemize}
        \item Emphasizes the necessity of high-quality random number generators to ensure the accuracy of simulations.
        \item Example: Discussing the impact of poor random number generation on the reliability of simulation results.
    \end{itemize}
\end{itemize}

% Challenges and Limitations
\begin{mdframed}[style=detailsstyle, title=Challenges and Limitations]
    \begin{itemize}
        \item \textbf{Monte Carlo Simulation:} Requires a large number of samples for accuracy, which can be computationally intensive.
        \item \textbf{Queuing Models:} Assumptions made in the model may not reflect real-world complexities, leading to inaccuracies.
        \item \textbf{Stock Market Simulation:} Market behavior is influenced by numerous unpredictable factors, making accurate predictions challenging.
        \item \textbf{Random Number Generation:} Poorly designed generators can introduce bias, affecting the validity of simulation outcomes.
    \end{itemize}
\end{mdframed}
